---
title: Homework 1 - Part 3
subtitle: R Basics
date: last-modified

author: YOUR_NAME

execute: 
  eval: true
  echo: true
  warning: false
  message: false

from: markdown+emoji
---

```{r setup}
library(tidyverse)
library(skimr)
```

# Direction
- Please address all questions in **Homework Assignment 1: Part 3** in this Quarto document.
  - Do not forget providing your name in Line 6 in the YAML header.

- Save this Quarto document with the name below:
  - `danl-200-hw1-LASTNAME-FIRSTNAME.qmd`\
  ( e.g., `danl-200-hw1-choe-byeonghak.qmd`)

- Please submit your Quarto document for Homework Assignment 1: Part 3 to the Brightspace.

- The due is February 20, 2024, 2:00 P.M.

- Please send Byeong-Hak an email (bchoe@geneseo.edu) if you have any questions.


<br>

# Part 3. R Basics

## Question 0.
Provide your GitHub username.

*Answer*:



<br><br>


## Question 1.
base-R provides the R object `state.name`. Write an R code to assign `state.name` to a variable, `US_states`.

*Answer*:
```{r}

```

<br><br>

## Question 2.
The `temp_F` vector contains the average high temperatures in January for the following cities: Seoul, Lagos, Paris, Rio de Janeiro, San Juan, and Rochester.

```{r}
temp_F <- c(35, 88, 42, 84, 81, 30)
```

Create a new vector named `temp_C` that stores the converted Celsius temperatures. Below is the conversion formula:

$$
C = \frac{5}{9}\times(F - 32)
$$

*Answer*:
```{r}

```

<br><br>


## Question 3.
- Write an R code to calculate the standard deviation (SD) of the integer vector `x` below manually. That is to calculate the SD without using the `sd()` function.

```{r}
x <- 1:25
```

- Also, write an R code to test whether the standard deviation you calculate manually above is equal to `sd(x)`.



*Answer*:
```{r}


```

<br><br>


## Question 4.
- Write an R code to read the CSV file, `https://bcdanl.github.io/data/mlb_teams.csv` using the `tidyverse`'s `read_csv()` function, and assign it to `MLB_teams`.

*Answer*:
```{r}

```

<br><br>


## Question 5.
Write an R code to provide summary statistics---mean, standard deviation, minimum, first quartile, median, third quartile, and maximum---for variables in the `MLB_teams` data.frame.

*Answer*:
```{r}

```

<br><br><br>


